\bf A HIERARCHICAL FAILURE-TIME MODEL FOR OBSERVATIONAL DATA EXHIBITING INFANT-MORTALITY AND WEAROUT FAILURE MODES

### 2018-04-08 paper/paper.tex
Report consistent number of sigfigs in table
Edits bibtek and model selection section

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\if0\blind
{
  \title{\bf A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes}
  \author{Eric Mittman\thanks{Department of Statistics, Iowa State University}\\
    and \\
    Colin Lewis-Beck\footnotemark[1]\\
    and \\
    William Q. Meeker\footnotemark[1]}
  \maketitle
} \fi

@@

\newpage
\tableofcontents
\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there is a need for models that can accomodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrr}
  \hline
 & 2.5\% & 50\% & 97.5\% \\ 
  \hline
$\pi$ & 0.03 & 0.05 & 0.10 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{0.5,1}$ & 1,029.42 & 2,279.09 & 3,989.76 \\ 
  $t_{0.2,2}$ & 18,010.30 & 18,273.22 & 18,553.22 \\ 
   \hline
\end{tabular}
\caption{Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.}
\label{table:1}
\end{table}

@@

\section{Supplementary Material}
\label{sec:supple}

\begin{description}

\item[Stan Code and Plots] Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6 (supplementary.pdf)

\item[Backblaze hard-drive data] Lifetime data set for all 44 drive-models used in our analysis. (backblaze\_hd\_data.csv)

\end{description}

>>>>

%\documentclass[12pt]{article}
\documentclass[aap]{imsart}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf,float, bm, subcaption, url, imsart}
\graphicspath{C:/Users/Colin/Documents/GitHub/BB_data_analysis/paper/fig/}
\usepackage{enumerate}
\usepackage{natbib}
\bibliographystyle{asa}
\usepackage{url} % not crucial - just used below for the URL

@@

\if0\blind
{
  \title{\bf A HIERARCHICAL FAILURE-TIME MODEL FOR OBSERVATIONAL DATA EXHIBITING INFANT-MORTALITY AND WEAROUT FAILURE MODES}
  \author{Eric Mittman and Colin Lewis-Beck and William Q. Meeker\\
	\textit{Iowa State University}}
  \maketitle
} \fi

@@

\newpage
%\tableofcontents
\newpage
\spacingset{1.45} % DON'T change the spacing!
\section{Introduction}
Consumers have an interest in accurate assessment of product reliability. Toward this end, there is a need for models that can accomodate common failure patterns and methods which can make the most of available data and properly account for uncertainty. Doing these things well enables good decision-making in matters related to product life, including purchase decisions and contingency planning.
%While computationally convenient, simple lifetime models can fail at each of these.

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrr}
  \hline
 & 2.5\% & 50\% & 97.5\% \\ 
  \hline
$\pi$ & 0.033 & 0.054 & 0.099 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{0.5,1}$ & $1.03\times 10^3$  & $2.28 \times 10^3$ & $3.99 \times 10^3$\\ 
  $t_{0.2,2}$ & $1.80 \times 10^4$ & $1.82 \times 10^4$ & $1.86 \times 10^4$ \\ 
   \hline
\end{tabular}
\caption{Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.}
\label{table:1}
\end{table}

@@

\section{Online Supplementary Material}
\label{sec:supple}
\begin{supplement}[id=suppA]
  \sname{Supplement A}
  \stitle{Stan Code and Plots}
  \slink[doi]{COMPLETED BY THE TYPESETTER}
  \sdatatype{.pdf}
  \sdescription{Stan code for Model 4 as well as the complete set of plots for Figures 5 and 6}
\end{supplement}

\begin{supplement}[id=suppB]
  \sname{Supplement B}
  \stitle{Backblaze Data}
  \slink[doi]{COMPLETED BY THE TYPESETTER}
  \sdatatype{.csv}
  \sdescription{Lifetime data set for all 44 drive-models used in our analysis.}
\end{supplement}
